### 2019-01-03 tex/appendix.tex
Corrected dangling words.

{\lemma Given any submodular extension $F(.)$ of an hierachical Potts energy function $E(.)$, its Lovasz extension $f(.)$ defines an LP relaxation of the corresponding MAP estimation problem as
\begin{align}
    \min_{{\bf z} \in \Delta'} f({\bf z}) 
\end{align}
%\label{lemma:lovasz_lp_metric}}

>>>>

{\lemma Given any submodular extension $F(.)$ of an hierarchical Potts energy function $E(.)$, its Lovasz extension $f(.)$ defines an LP relaxation of the corresponding MAP estimation problem as
\begin{align}
    \min_{{\bf z} \in \Delta'} f({\bf z}) 
\end{align}
%\label{lemma:lovasz_lp_metric}}

### 2019-01-03 tex/paper.tex
Corrected dangling words.

The energy function can be interpreted as defining a probability distribution $P({\bf x})$ as follows:
\begin{equation}
    P({\bf x}) =
    \begin{cases}
        \frac{1}{\mathcal{Z}} \exp(-E({\bf x})) & \quad \text{if} \enskip {\bf x} \in {\mathcal L}^N,\\
       0  & \quad \text{otherwise}. \\
    \end{cases}
\label{eq:crf_prob_distrib}
\end{equation}
The normalization factor $Z = \sum_{{\bf x} \in {\mathcal L}^N} \exp(-E({\bf x}))$ is known as the {\it partition function}.

@@

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with accurate extensions for different classes of CRF energy functions? Is it possible to identify optimal extensions which yield the tightest bound?

@@

Our extensions are derived from LP relaxations. When the LP relaxation is the
tightest possible, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This is to say that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, 
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the
extension is best for every instance of the energy function. It may be possible
to solve an optimisation problem to obtain the best extension for every given
instance of energy $E(.)$. However, in this paper, we do not take that approach, and instead provide a general solution for a given class of energy function.

In subsection \ref{subsec:potts}, we prove the worst-case optimality of the submodular extension used in literature for the Potts model. In subsection \ref{subsec:hier_potts}, we obtain worst-case optimal submodular extension for the more general hierarchical Potts model. Finally, in subsection \ref{subsec:dense_crf}, we provide an approach to make our inference algorithm efficient for the dense CRF model. Using our approach, the inference algorithm has linear time-complexity in the number of variables and labels.

@@

\begin{figure}
\centering
\includegraphics[scale = 0.35]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows the way to compute the extension
values of the set $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:potts_extension_example}
\end{figure}

>>>>

The energy function can be interpreted as defining a probability distribution $P({\bf x})$ as:
\begin{equation}
    P({\bf x}) =
    \begin{cases}
        \frac{1}{\mathcal{Z}} \exp(-E({\bf x})) & \quad \text{if} \enskip {\bf x} \in {\mathcal L}^N,\\
       0  & \quad \text{otherwise}. \\
    \end{cases}
\label{eq:crf_prob_distrib}
\end{equation}
The normalization factor $Z = \sum_{{\bf x} \in {\mathcal L}^N} \exp(-E({\bf x}))$ is known as the {\it partition function}.

@@

Different choices of extensions $F$ change the domain in problem \eqref{eq:min_upper_bound}, leading to different upper bounds on the log-partition function. How does one come up with accurate extensions for different classes of CRF energy? Is it possible to identify optimal extensions which yield the tightest bound?

@@

Our extensions are derived from LP relaxations. When the LP relaxation is the
tightest possible, the extension family ${\mathcal
F}_{opt}$ we obtain is \emph{worst-case optimal}. This is to say that there does not
exist another submodular extension family ${\mathcal F}$ that gives a tighter
upper bound for problem \eqref{eq:min_upper_bound} than ${\mathcal F}_{opt}$
for all instances of the energy function in $\mathcal E$. Formally, ${\mathcal F}_{opt}$ is worst-case optimal if
\begin{equation}
    \nexists {\mathcal F}: \min_{{\bf s} \in EP({\mathcal F}(E))} g({\bf s})
    \leq \min_{{\bf s} \in EP({\mathcal F}_{opt}(E))} g({\bf s}) \enspace
    \forall \; E(.) \in \mathcal E.
    \label{eq:best_submod}
\end{equation}
Note that the notion of worst-case optimality does not guarantee that the
extension is best for every instance of the energy function. It may be possible
to solve an optimisation problem to obtain the best extension for every given
instance of energy $E(.)$. However, in this paper, we do not take that approach, and instead provide a general solution for a given class of energy function.

In subsection \ref{subsec:potts}, we prove the worst-case optimality of the submodular extension used in literature for the Potts model. In subsection \ref{subsec:hier_potts}, we obtain worst-case optimal submodular extension for the more general hierarchical Potts model. Finally, in subsection \ref{subsec:dense_crf}, we provide a way to make our inference algorithm efficient for the dense CRF model. Using our approach, the inference algorithm has linear time-complexity in the number of variables and labels.

@@

\begin{figure}
\centering
\includegraphics[scale = 0.35]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows how to compute extension for $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:potts_extension_example}
\end{figure}
